An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2022-05-30 poly-embed-journal/poly-embed-journal.tex
Adding parag in 6.3

\raf{Short parag on why we care about trim}

>>>>

\raf{Short parag on why we care about trim}\jessie{Attempted; burn? i don't like this.}
Trimmed losses allow us to understand ``where the action happens'' even in the best case scenario where the loss vector is optimal for \emph{some} data distribution. \jessie{phrasing}
In what follows, we relate the trimmed form of a loss to the concept of redundancy in property elicitation.
